---
title: ""
output: 
  html_document:
      toc: false
      theme: lumen 
      toc_float: true
      toc_depth: 4
      df_print: paged
editor_options: 
  chunk_output_type: console
---



<!-- CSS style -->
<style>
body {
position: relative;
left: 42px;}
.main-container {max-width: none !important;}
table, td, th {
align: left;
font-size: 11px;
border: none;
padding-left: 5em;
padding-right: 5em;
min-width: 100%;
word-wrap: break-word;
max-width: 240px;
margin-left: auto;
margin-right: auto;
margin-top: 1em;
margin-bottom: 1em;
}
</style>




```{r setup, include=F}
knitr::opts_chunk$set(echo = TRUE,comment = '',warning=F,error = F)
options(width = 1200)
```

# {.tabset .tabset-pills}


```{r, echo=F, include=FALSE}

{
    library(data.table)
    library(ggplot2); theme_set(theme_bw())
    library(ggrepel)
    library(patchwork)
    library(stringr)
    
    noise <- function(data) {
        m <- mapd(data)
        f <- 2^m-1
        return(round(100*f,2))
    }
    
    mapd <- function(data) {
        return(median(abs(diff(data))))
    } 
    
}
```



## Genome {.active}


```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=15,fig.width=17}

# Print tumor sample frankenplot (with somatic mutations)
name <- basename(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins_t
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t
strvs <- t_strvs
purecn <- purecn_stat

p <- genomeplot(name, targets, segments, snps, somatic, germline, strvs, purecn, dpyd_result)



#save.image('~/Analysis/ALASCCA/temp.Rdata')

if (!is.null(opts$output_figure)) if (!is.na(opts$output_figure)) {
    
    stats <- paste0('Coverage: ',
                    paste(round(quantile(snps$depth,c(.1,.9),na.rm=T)),collapse = '-')
    )
    stats <- paste0(stats,', DPYD: ', ifelse(is.null(dpyd_result),'NA',dpyd_result$genotype))
    
    if (!is.null(purecn)) try( {
        stats <- paste0(stats,', PureCN: ',round(purecn$Ploidy,1),'N, ',100*purecn$Purity,'%')
    }, silent=T)
    
    date <- format(Sys.time(), "%a %b %e %Y, %H:%M")
    
    pa <- plot_annotation(
        title = paste(basename(name),'  ',date,'  ',stats)
    )
    
    png(filename = opts$output_figure, width = 14, height = 8, units = 'in', res=150)
    
    layout <-  "ABBBB
                CDDDD
                EFFFF"
    fig <-
        p$gc_rawdepth+p$pos_rawdepth+
        p$gc_log2+p$pos_log2+
        p$depth_alleleratio+p$pos_alleleratio+
        plot_layout(design = layout,guides = 'collect')
    
    print(fig+pa)
    dev.off()
}
```


---


```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=15,fig.width=17}


if (!t_only) { # print normal sample frankenplot (without mutations)
    name <- basename(str_remove(opts$normal_cnr,'.cnr'))
    targets <- bins_n
    segments <- segments_n
    snps <- alf_n
    somatic <- NULL
    germline <- galf_n
    strvs <- NULL
    purecn <- NULL
    
    q <- genomeplot(name, targets, segments, snps, somatic, germline, strvs, purecn, dpyd_result)
    
}

```

---


## HRD


```{r, echo=FALSE, fig.keep='all', message=FALSE, fig.height=5,fig.width=13}

name <- basename(str_remove(opts$tumor_cnr,'.cnr'))

hrdplot(hrdtable,p)

print(as.data.table(gis_model(NULL)))

print(hrdtable[feature=='predicted_gis',.(sample,feature,fraction,value)])


```

## DPYD

### Genotyping result

```{r, echo=FALSE, fig.keep='all', message=FALSE, fig.height=5,fig.width=10}

if (!is.null(dpyd_result)) {
    
    print(paste0('DPYD genotyping result: ',dpyd_result$genotype[1],'. ',dpyd_result$text,''))
    
    g <- ggplot(dpyd_table) + xlab('Allele count') + ylab('Allele ratio') +
        geom_point(aes(x=count,y=variant_ratio,fill=alias,shape=allele)) +
        scale_shape_manual(values=c('wt'=22,'alt'=21)) +
        facet_grid(rows = vars(allele), cols = vars(file)) +
        guides(fill=guide_legend(override.aes=list(shape=21,size=2)))
    print(g)
    
}

```

### Evidence

```{r, echo=FALSE, fig.keep='all', message=FALSE}

print(as.list(dpyd_result))

#if (!is.null(dpyd_table)) 
#knitr::kable(dpyd_table[,1:24], "html") %>%
# kable_styling(
#     bootstrap_options = c("striped", "hover", "condensed"),
#     full_width = F  
# ) %>%
# column_spec(column = 1, width = "5em") %>% 
# scroll_box(width = "100%", extra_css = "white-space: nowrap;")

# kable(dpyd_table[,1:24], "html", booktabs = TRUE) %>%
# kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
# scroll_box(width = "100%")
if (!is.null(dpyd_table)) 
    kable(dpyd_table[,1:24], "html", booktabs = TRUE) %>%
    kable_styling(
        bootstrap_options = c("striped", "hover", "condensed"),
        full_width = FALSE
    ) %>%
    # Add this line to prevent text wrapping in all 24 columns
    column_spec(1:24, extra_css = "white-space: nowrap;") %>%
    scroll_box(width = "80%")

```


## 1 {#chr1} 


```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

chr <- 1

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins_t
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}



if (!t_only) { # print normal sample chromosome
    name <- paste(str_remove(opts$normal_cnr,'.cnr'))
    targets <- bins_n
    segments <- segments_n
    snps <- alf_n
    somatic <- NULL
    germline <- galf_n
    
    chromplot(chr, name, targets, segments, snps, somatic, germline)
    
}

```



## 2 {#chr2}

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

chr <- 2

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins_t
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

if (!t_only) { # print normal sample chromosome
    name <- paste(str_remove(opts$normal_cnr,'.cnr'))
    targets <- bins_n
    segments <- segments_n
    snps <- alf_n
    somatic <- NULL
    germline <- galf_n 
    
    chromplot(chr, name, targets, segments, snps, somatic, germline)
    
}
```


## 3 {#chr3}

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

chr <- 3

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins_t
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

if (!t_only) { # print normal sample chromosome
    name <- paste(str_remove(opts$normal_cnr,'.cnr'))
    targets <- bins_n
    segments <- segments_n
    snps <- alf_n
    somatic <- NULL
    germline <- galf_n 
    
    chromplot(chr, name, targets, segments, snps, somatic, germline)
    
}
```


## 4 {#chr4}

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

chr <- 4

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins_t
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

if (!t_only) { # print normal sample chromosome
    name <- paste(str_remove(opts$normal_cnr,'.cnr'))
    targets <- bins_n
    segments <- segments_n
    snps <- alf_n
    somatic <- NULL
    germline <- galf_n 
    
    chromplot(chr, name, targets, segments, snps, somatic, germline)
}

```


## 5 {#chr5} 

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

chr <- 5

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins_t
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

if (!t_only) { # print normal sample chromosome
    name <- paste(str_remove(opts$normal_cnr,'.cnr'))
    targets <- bins_n
    segments <- segments_n
    snps <- alf_n
    somatic <- NULL
    germline <- galf_n 
    
    chromplot(chr, name, targets, segments, snps, somatic, germline)
    
}
```


## 6 {#chr6}

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

chr <- 6

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins_t
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

if (!t_only) { # print normal sample chromosome
    name <- paste(str_remove(opts$normal_cnr,'.cnr'))
    targets <- bins_n
    segments <- segments_n
    snps <- alf_n
    somatic <- NULL
    germline <- galf_n 
    
    chromplot(chr, name, targets, segments, snps, somatic, germline)
}

```


## 7 {#chr7} 

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

chr <- 7

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins_t
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

if (!t_only) { # print normal sample chromosome
    name <- paste(str_remove(opts$normal_cnr,'.cnr'))
    targets <- bins_n
    segments <- segments_n
    snps <- alf_n
    somatic <- NULL
    germline <- galf_n 
    
    chromplot(chr, name, targets, segments, snps, somatic, germline)
}

```


## 8 {#chr8} 

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

chr <- 8

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins_t
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

if (!t_only) { # print normal sample chromosome
    name <- paste(str_remove(opts$normal_cnr,'.cnr'))
    targets <- bins_n
    segments <- segments_n
    snps <- alf_n
    somatic <- NULL
    germline <- galf_n 
    
    chromplot(chr, name, targets, segments, snps, somatic, germline)
}

```


## 9 {#chr9} 

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

chr <- 9

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins_t
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

if (!t_only) { # print normal sample chromosome
    name <- paste(str_remove(opts$normal_cnr,'.cnr'))
    targets <- bins_n
    segments <- segments_n
    snps <- alf_n
    somatic <- NULL
    germline <- galf_n 
    
    chromplot(chr, name, targets, segments, snps, somatic, germline)
}

```


## 10 {#chr10}

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

chr <- 10

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins_t
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

if (!t_only) { # print normal sample chromosome
    name <- paste(str_remove(opts$normal_cnr,'.cnr'))
    targets <- bins_n
    segments <- segments_n
    snps <- alf_n
    somatic <- NULL
    germline <- galf_n 
    
    chromplot(chr, name, targets, segments, snps, somatic, germline)
    
}
```


## 11 {#chr11} 

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

chr <- 11

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins_t
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

if (!t_only) { # print normal sample chromosome
    name <- paste(str_remove(opts$normal_cnr,'.cnr'))
    targets <- bins_n
    segments <- segments_n
    snps <- alf_n
    somatic <- NULL
    germline <- galf_n 
    
    chromplot(chr, name, targets, segments, snps, somatic, germline)
}

```


## 12 {#chr12} 

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

chr <- 12

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins_t
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

if (!t_only) { # print normal sample chromosome
    name <- paste(str_remove(opts$normal_cnr,'.cnr'))
    targets <- bins_n
    segments <- segments_n
    snps <- alf_n
    somatic <- NULL
    germline <- galf_n 
    
    chromplot(chr, name, targets, segments, snps, somatic, germline)
}

```


## 13 {#chr13} 

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

chr <- 13

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins_t
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

if (!t_only) { # print normal sample chromosome
    name <- paste(str_remove(opts$normal_cnr,'.cnr'))
    targets <- bins_n
    segments <- segments_n
    snps <- alf_n
    somatic <- NULL
    germline <- galf_n 
    
    chromplot(chr, name, targets, segments, snps, somatic, germline)
}

```


## 14 {#chr14}

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

chr <- 14

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins_t
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

if (!t_only) { # print normal sample chromosome
    name <- paste(str_remove(opts$normal_cnr,'.cnr'))
    targets <- bins_n
    segments <- segments_n
    snps <- alf_n
    somatic <- NULL
    germline <- galf_n 
    
    chromplot(chr, name, targets, segments, snps, somatic, germline)
}

```


## 15 {#chr15}

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

chr <- 15

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins_t
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

if (!t_only) { # print normal sample chromosome
    name <- paste(str_remove(opts$normal_cnr,'.cnr'))
    targets <- bins_n
    segments <- segments_n
    snps <- alf_n
    somatic <- NULL
    germline <- galf_n 
    
    chromplot(chr, name, targets, segments, snps, somatic, germline)
}

```


## 16 {#chr16}

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

chr <- 16

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins_t
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

if (!t_only) { # print normal sample chromosome
    name <- paste(str_remove(opts$normal_cnr,'.cnr'))
    targets <- bins_n
    segments <- segments_n
    snps <- alf_n
    somatic <- NULL
    germline <- galf_n 
    
    chromplot(chr, name, targets, segments, snps, somatic, germline)
}

```


## 17 {#chr17} 

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

chr <- 17

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins_t
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

if (!t_only) { # print normal sample chromosome
    name <- paste(str_remove(opts$normal_cnr,'.cnr'))
    targets <- bins_n
    segments <- segments_n
    snps <- alf_n
    somatic <- NULL
    germline <- galf_n 
    
    chromplot(chr, name, targets, segments, snps, somatic, germline)
}

```


## 18 {#chr18} 

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

chr <- 18

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins_t
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

if (!t_only) { # print normal sample chromosome
    name <- paste(str_remove(opts$normal_cnr,'.cnr'))
    targets <- bins_n
    segments <- segments_n
    snps <- alf_n
    somatic <- NULL
    germline <- galf_n 
    
    chromplot(chr, name, targets, segments, snps, somatic, germline)
}

```


## 19 {#chr19} 

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

chr <- 19

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins_t
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

if (!t_only) { # print normal sample chromosome
    name <- paste(str_remove(opts$normal_cnr,'.cnr'))
    targets <- bins_n
    segments <- segments_n
    snps <- alf_n
    somatic <- NULL
    germline <- galf_n 
    
    chromplot(chr, name, targets, segments, snps, somatic, germline)
}

```


## 20 {#chr20} 

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

chr <- 20

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins_t
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

if (!t_only) { # print normal sample chromosome
    name <- paste(str_remove(opts$normal_cnr,'.cnr'))
    targets <- bins_n
    segments <- segments_n
    snps <- alf_n
    somatic <- NULL
    germline <- galf_n 
    
    chromplot(chr, name, targets, segments, snps, somatic, germline)
}

```


## 21 {#chr21} 

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

chr <- 21

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins_t
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

if (!t_only) { # print normal sample chromosome
    name <- paste(str_remove(opts$normal_cnr,'.cnr'))
    targets <- bins_n
    segments <- segments_n
    snps <- alf_n
    somatic <- NULL
    germline <- galf_n 
    
    chromplot(chr, name, targets, segments, snps, somatic, germline)
}

```


## 22 {#chr22} 

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

chr <- 22

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins_t
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

if (!t_only) { # print normal sample chromosome
    name <- paste(str_remove(opts$normal_cnr,'.cnr'))
    targets <- bins_n
    segments <- segments_n
    snps <- alf_n
    somatic <- NULL
    germline <- galf_n 
    
    chromplot(chr, name, targets, segments, snps, somatic, germline)
    
}
```


## X {#chrX}

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

chr <- 'X'

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins_t
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=16,fig.width=16}

if (!t_only) { # print normal sample chromosome
    name <- paste(str_remove(opts$normal_cnr,'.cnr'))
    targets <- bins_n
    segments <- segments_n
    snps <- alf_n
    somatic <- NULL
    germline <- galf_n; 
    
    chromplot(chr, name, targets, segments, snps, somatic, germline)
    
}
```


## Data {.tabset}

### Small Somatic

```{r, echo=FALSE}

t <- salf[IMPACT %in% c('MODERATE','HIGH') | str_detect(CLIN_SIG,'athogenic') | is_hotspot==T | str_detect(Consequence,'splice')]
if (!is.null(salf)) knitr::kable(t, "html") %>%
    kable_styling(
        bootstrap_options = c("striped", "hover", "condensed"),
        full_width = TRUE
    ) %>%
    column_spec(column = 1, width = "5em") %>%
    scroll_box(width = "100%", extra_css = "white-space: nowrap;")

```

### Files {.active}

Arguments to call:

```{r, echo=FALSE}


cat(paste(paste0('--',names(opts[-1])),' \\ \n',opts[-1], collapse = ' \\ \n'))

cat('\n')

cat('opts <-')
dput(opts)


print(sessionInfo())


```
