---
title: ""
output: 
  html_document:
      toc: false
      theme: lumen 
      toc_float: true
      toc_depth: 4
      df_print: paged
editor_options: 
  chunk_output_type: console
---



<!-- CSS style -->
<style>
body {
position: relative;
left: 42px;}
.main-container {max-width: none !important;}
table, td, th {
align: left;
font-size: 11px;
border: none;
padding-left: 5em;
padding-right: 5em;
min-width: 100%;
word-wrap: break-word;
max-width: 240px;
margin-left: auto;
margin-right: auto;
margin-top: 1em;
margin-bottom: 1em;
}
</style>




```{r setup, include=F}
knitr::opts_chunk$set(echo = TRUE,comment = '',warning=F,error = F)
options(width = 1200)
```

# {.tabset .tabset-pills}


```{r, echo=F, include=FALSE}

{
    library(data.table)
    library(ggplot2); theme_set(theme_bw())
    library(ggrepel)
    library(patchwork)
    library(stringr)
    
    noise <- function(data) {
        m <- mapd(data)
        f <- 2^m-1
        return(round(100*f,2))
    }
    
    mapd <- function(data) {
        return(median(abs(diff(data))))
    } 
    
}
```



## Genome


```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=15,fig.width=17}

# Print tumor sample frankenplot (with somatic mutations)
name <- basename(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t
strvs <- t_strvs
purecn <- purecn_stat

genomeplot(name, targets, segments, snps, somatic, germline, strvs, purecn)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=15,fig.width=17}


# if there is a normal...

# print normal sample frankenplot (without mutations)
name <- basename(str_remove(opts$normal_cnr,'.cnr'))
targets <- bins_n
segments <- segments_n
snps <- alf_n
somatic <- NULL
germline <- galf_n
strvs <- NULL
purecn <- NULL

genomeplot(name, targets, segments, snps, somatic, germline, strvs, purecn)


```



<!-- Gene shortcuts: [AR](#chrX) [ATM](#chr11) [PTEN](#chr10) -->


<!-- ## Purity {.tabset} -->

<!-- ### High -->

<!-- ### Low -->

<!-- ## HRD -->

## 1 {#chr1} 

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

chr <- 1

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

# print normal sample chromosome
name <- paste(str_remove(opts$normal_cnr,'.cnr'))
targets <- bins_n
segments <- segments_n
snps <- alf_n
somatic <- NULL
germline <- galf_n

chromplot(chr, name, targets, segments, snps, somatic, germline)


```



## 2 {#chr2}

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

chr <- 2

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

# print normal sample chromosome
name <- paste(str_remove(opts$normal_cnr,'.cnr'))
targets <- bins_n
segments <- segments_n
snps <- alf_n
somatic <- NULL
germline <- galf_n 

chromplot(chr, name, targets, segments, snps, somatic, germline)


```


## 3 {#chr3}

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

chr <- 3

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

# print normal sample chromosome
name <- paste(str_remove(opts$normal_cnr,'.cnr'))
targets <- bins_n
segments <- segments_n
snps <- alf_n
somatic <- NULL
germline <- galf_n 

chromplot(chr, name, targets, segments, snps, somatic, germline)


```


## 4 {#chr4}

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

chr <- 4

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

# print normal sample chromosome
name <- paste(str_remove(opts$normal_cnr,'.cnr'))
targets <- bins_n
segments <- segments_n
snps <- alf_n
somatic <- NULL
germline <- galf_n 

chromplot(chr, name, targets, segments, snps, somatic, germline)


```


## 5 {#chr5} 

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

chr <- 5

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

# print normal sample chromosome
name <- paste(str_remove(opts$normal_cnr,'.cnr'))
targets <- bins_n
segments <- segments_n
snps <- alf_n
somatic <- NULL
germline <- galf_n 

chromplot(chr, name, targets, segments, snps, somatic, germline)


```


## 6 {#chr6}

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

chr <- 6

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

# print normal sample chromosome
name <- paste(str_remove(opts$normal_cnr,'.cnr'))
targets <- bins_n
segments <- segments_n
snps <- alf_n
somatic <- NULL
germline <- galf_n 

chromplot(chr, name, targets, segments, snps, somatic, germline)


```


## 7 {#chr7} 

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

chr <- 7

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

# print normal sample chromosome
name <- paste(str_remove(opts$normal_cnr,'.cnr'))
targets <- bins_n
segments <- segments_n
snps <- alf_n
somatic <- NULL
germline <- galf_n 

chromplot(chr, name, targets, segments, snps, somatic, germline)


```


## 8 {#chr8} 

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

chr <- 8

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

# print normal sample chromosome
name <- paste(str_remove(opts$normal_cnr,'.cnr'))
targets <- bins_n
segments <- segments_n
snps <- alf_n
somatic <- NULL
germline <- galf_n 

chromplot(chr, name, targets, segments, snps, somatic, germline)


```


## 9 {#chr9} 

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

chr <- 9

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

# print normal sample chromosome
name <- paste(str_remove(opts$normal_cnr,'.cnr'))
targets <- bins_n
segments <- segments_n
snps <- alf_n
somatic <- NULL
germline <- galf_n 

chromplot(chr, name, targets, segments, snps, somatic, germline)


```


## 10 {#chr10}

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

chr <- 10

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

# print normal sample chromosome
name <- paste(str_remove(opts$normal_cnr,'.cnr'))
targets <- bins_n
segments <- segments_n
snps <- alf_n
somatic <- NULL
germline <- galf_n 

chromplot(chr, name, targets, segments, snps, somatic, germline)


```


## 11 {#chr11} 

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

chr <- 11

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

# print normal sample chromosome
name <- paste(str_remove(opts$normal_cnr,'.cnr'))
targets <- bins_n
segments <- segments_n
snps <- alf_n
somatic <- NULL
germline <- galf_n 

chromplot(chr, name, targets, segments, snps, somatic, germline)


```


## 12 {#chr12} 

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

chr <- 12

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

# print normal sample chromosome
name <- paste(str_remove(opts$normal_cnr,'.cnr'))
targets <- bins_n
segments <- segments_n
snps <- alf_n
somatic <- NULL
germline <- galf_n 

chromplot(chr, name, targets, segments, snps, somatic, germline)


```


## 13 {#chr13} 

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

chr <- 13

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

# print normal sample chromosome
name <- paste(str_remove(opts$normal_cnr,'.cnr'))
targets <- bins_n
segments <- segments_n
snps <- alf_n
somatic <- NULL
germline <- galf_n 

chromplot(chr, name, targets, segments, snps, somatic, germline)


```


## 14 {#chr14}

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

chr <- 14

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

# print normal sample chromosome
name <- paste(str_remove(opts$normal_cnr,'.cnr'))
targets <- bins_n
segments <- segments_n
snps <- alf_n
somatic <- NULL
germline <- galf_n 

chromplot(chr, name, targets, segments, snps, somatic, germline)


```


## 15 {#chr15}

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

chr <- 15

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

# print normal sample chromosome
name <- paste(str_remove(opts$normal_cnr,'.cnr'))
targets <- bins_n
segments <- segments_n
snps <- alf_n
somatic <- NULL
germline <- galf_n 

chromplot(chr, name, targets, segments, snps, somatic, germline)


```


## 16 {#chr16}

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

chr <- 16

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

# print normal sample chromosome
name <- paste(str_remove(opts$normal_cnr,'.cnr'))
targets <- bins_n
segments <- segments_n
snps <- alf_n
somatic <- NULL
germline <- galf_n 

chromplot(chr, name, targets, segments, snps, somatic, germline)


```


## 17 {#chr17} 

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

chr <- 17

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

# print normal sample chromosome
name <- paste(str_remove(opts$normal_cnr,'.cnr'))
targets <- bins_n
segments <- segments_n
snps <- alf_n
somatic <- NULL
germline <- galf_n 

chromplot(chr, name, targets, segments, snps, somatic, germline)


```


## 18 {#chr18} 

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

chr <- 18

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

# print normal sample chromosome
name <- paste(str_remove(opts$normal_cnr,'.cnr'))
targets <- bins_n
segments <- segments_n
snps <- alf_n
somatic <- NULL
germline <- galf_n 

chromplot(chr, name, targets, segments, snps, somatic, germline)


```


## 19 {#chr19} 

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

chr <- 19

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

# print normal sample chromosome
name <- paste(str_remove(opts$normal_cnr,'.cnr'))
targets <- bins_n
segments <- segments_n
snps <- alf_n
somatic <- NULL
germline <- galf_n 

chromplot(chr, name, targets, segments, snps, somatic, germline)


```


## 20 {#chr20} 

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

chr <- 20

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

# print normal sample chromosome
name <- paste(str_remove(opts$normal_cnr,'.cnr'))
targets <- bins_n
segments <- segments_n
snps <- alf_n
somatic <- NULL
germline <- galf_n 

chromplot(chr, name, targets, segments, snps, somatic, germline)


```


## 21 {#chr21} 

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

chr <- 21

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

# print normal sample chromosome
name <- paste(str_remove(opts$normal_cnr,'.cnr'))
targets <- bins_n
segments <- segments_n
snps <- alf_n
somatic <- NULL
germline <- galf_n 

chromplot(chr, name, targets, segments, snps, somatic, germline)


```


## 22 {#chr22} 

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

chr <- 22

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

# print normal sample chromosome
name <- paste(str_remove(opts$normal_cnr,'.cnr'))
targets <- bins_n
segments <- segments_n
snps <- alf_n
somatic <- NULL
germline <- galf_n 

chromplot(chr, name, targets, segments, snps, somatic, germline)


```


## X {#chrX}

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

chr <- 'X'

# Print tumor sample chromosome
name <- paste(str_remove(opts$tumor_cnr,'.cnr'))
targets <- bins
segments <- segments_t
snps <- alf
somatic <- salf
germline <- galf_t

chromplot(chr, name, targets, segments, snps, somatic, germline)

```

---

```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16}

# print normal sample chromosome
name <- paste(str_remove(opts$normal_cnr,'.cnr'))
targets <- bins_n
segments <- segments_n
snps <- alf_n
somatic <- NULL
germline <- galf_n; 

chromplot(chr, name, targets, segments, snps, somatic, germline)


```


<!-- ## Y {#chrY} -->

<!-- ```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16} -->

<!-- chr <- 'Y' -->

<!-- # Print tumor sample chromosome -->
<!-- name <- paste(str_remove(opts$tumor_cnr,'.cnr')) -->
<!-- targets <- bins -->
<!-- segments <- segments_t -->
<!-- snps <- alf -->
<!-- somatic <- salf -->
<!-- germline <- galf -->

<!-- chromplot(chr, name, targets, segments, snps, somatic, germline) -->

<!-- ``` -->

<!-- --- -->

<!-- ```{r, echo=FALSE, results='hide', fig.keep='all', message=FALSE, fig.height=8,fig.width=16} -->

<!-- # print normal sample chromosome -->
<!-- name <- paste(str_remove(opts$normal_cnr,'.cnr')) -->
<!-- targets <- bins_n -->
<!-- segments <- segments_n -->
<!-- snps <- alf_n -->
<!-- somatic <- NA -->
<!-- germline <- galf_n  -->

<!-- chromplot(chr, name, targets, segments, snps, somatic=NULL, germline=NULL) -->


<!-- ``` -->

























